### 2017-05-31 doc/conclusions.tex
discussion of generalizability was moved to the last section

\section{Conclusion}
\label{conclusion}

@@

>>>>

\section{Conclusion}
\label{sec:conclusion}

@@

\subsection{Generalizing to other architectures}

{\bf From 4.1 (computing omission scores):}

For other RNN architectures such as LSTMs \label{edit:omitgeneral}
and their bi-directional variants, measuring the contribution
of tokens to their predictions (or the omission scores)
can be straight-forwardly computed using their hidden state 
at the last time step used for prediction. Furthermore, the technique 
can be applied in general to other architectures which
map variable length linguistic expressions to the same fixed dimensional
space and perform predictions based on these embeddings. 
This includes tree-structured Recursive Neural Network models such as the Tree-LSTM
introduced in \namecite{kai2015treelstm} or the CNN architecture of \namecite{yoonneural2014} 
for sentence classification. In both cases the pre-softmax activations can be extracted 
from the models as the representations of the full and partial sentences.

{\bf From 4.3 (beyond lexical cues):}
The analysis we described here takes
the omission scores as input data, therefore it can be potentially applied 
to any architecture for which the omission scores can be computed. However,
the presented analysis and results regarding word positions can only be meaningful
for Recurrent Neural Networks as they compute their representations sequentially and are not
limited by fixed window sizes.\footnote{CNNs with multi-word filters
and tree-structured recursive neural networks do not incrementally build representations
of sentences in a left-to-right or right-to-left fashion. 
Bi-directional RNNs, on the other hand, are sensitive by word-order and can potentially
learn to handle the same word in different positions differently. \label{edit:foot}}

{\bf From old 6 (top-k-context), not sure if it's applicable to the mutual information measure:}
This method can be straight-forwardly applied to various 
RNN architectures such as Elman networks or LSTMs 
as it only requires storing the activation values for hidden units and 
their corresponding context. For architectures with $n$ hidden layers
one could extract multiple activation vectors $M_i^{1}, \ldots, M_i^{n}$
for each unit, and perform analysis on each of them separately.
A limitation of the generalizability of our analysis is that in the case of 
bi-directional architectures the interpretation of the features
extracted by the RNNs that process the input tokens in the reversed order
might be hard from a linguistic point of view.

A limitation of the generalizability of our 
analysis is that in the case of 
bi-directional architectures the interpretation of the features
extracted by the RNNs that process the input tokens in the reversed order
might be hard from a linguistic point of view.
